---
title: "UAV Stitching Summary"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    css: stitch_report.css
    self_contained: no
    smart: no
    lib_dir: libs
params:
  StitchID: ti_2018-02-17_flt01_stch01
---

```{r setup, include=FALSE}
## Setup
knitr::opts_chunk$set(echo = TRUE)
library(droneimg)
library(readxl)
library(rgdal)
library(leaflet)
library(dplyr)
```

```{r import_excel, include=FALSE}
## Import Mission Data
missionsDF <- read_excel("treas_island_missions.xlsx", sheet = "Missions")
stitchesDF <- read_excel("treas_island_missions.xlsx", sheet = "Stitches")

## Join tables and select stitching tasks
stch_msn <- dplyr::left_join(stitchesDF, missionsDF, by = "MissionID")

idx <- which(stitchesDF$StitchID == params$StitchID)
stchLst <- stch_msn[idx,] 
print(names(stchLst))
```

## `r stchLst$StitchTitle`

<span class="tagline">`r stchLst$MissionDescription`</span>

<div class="leftthird">
<span class="subhead">Flight Info</span>  
__Location__: `r stchLst$Location`  
__Date__: `r stchLst$Date`  
__Start time__: `r format(stchLst$StartTime,"%H:%M")`  
__End time__: `r format(stchLst$EndTime,"%H:%M")`  
</div>

<div class="rightthird">
<span class="subhead">Processing Settings</span>  
__Platform__: `r stchLst$StitchingPlatform`  
__StitchID__: `r stchLst$StitchID`  
__Parameter Preset__: `r stchLst$ParameterPreset`  
__Processing Time (min)__: `r stchLst$ProcessTimeMin`  
__Description__: `r stchLst$Description`  
</div>

<div class="rightthird">
<span class="subhead">Capture Settings</span>  
__Mission Type__: `r stchLst$MissionType`  
__Num images__: `r stchLst$NumImages`  
__Front overlap__: `r paste0(stchLst$OverlapFront, "%")`  
__Side overlap__: `r paste0(stchLst$OverlapSide, "%")`  
__Elevation (ft)__: `r stchLst$ElevationFt`  
__Expected GSD (in)__: `r stchLst$ExpectedGSDin`  
__Drone Speed__: `r stchLst$DroneSpeed`  
__Trigger mode__: `r stchLst$TriggerMode`  
__White balance__: `r stchLst$WhiteBalance`  
__Exposure__: `r stchLst$Exposure`  
</div>

<div class="killfloat"></div>

## Images {.tabset}

### Locations

```{r leaflet_ctr, echo=FALSE, message=FALSE}
## Initiate a new leaflet object
m <- leaflet(width="800px", height="600px")

## Add tiles properties
tilesURL = "http://server.arcgisonline.com/ArcGIS/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}"
tilesAttr = "Tiles &copy; Esri &mdash; Source: Esri, i-cubed, USDA, USGS, AEX, GeoEye, Getmapping, Aerogrid, IGN, IGP, UPR-EGP, and the GIS User Community"
m <- m %>% addTiles(tilesURL, attribution=tilesAttr)

## Read in image centroids
ptsUTM <- readOGR(dsn=dirname(stchLst$ImgShpPts), layer=basename(stchLst$ImgShpPts), verbose=FALSE)

## Reproject pts to lat-long (required by leaflet)
crsLatLong <- CRS("+proj=longlat +datum=WGS84")
ptsLL <- spTransform(geometry(ptsUTM), crsLatLong)

## Set the bounding box
ptsBBox <- bbox(ptsLL)
m_pts <- m %>% fitBounds(ptsBBox[1,1], ptsBBox[2,1], ptsBBox[1,2], ptsBBox[2,2])

## Add markers
m_pts <- m_pts %>% addCircleMarkers(data=ptsLL, radius=3, stroke=FALSE, fillColor="yellow", fillOpacity=1)

## Display HTML Widget
m_pts
```

### Footprints

```{r leaflet_fp, echo=FALSE, message=FALSE}
## Read in image centroids
fpUTM <- readOGR(dsn=dirname(stchLst$ImgShpFp), layer=basename(stchLst$ImgShpFp), verbose=FALSE)

## Reproject pts to lat-long (required by leaflet)
fpLL <- spTransform(geometry(fpUTM), crsLatLong)

## Set the bounding box
fpBBox <- bbox(fpLL)
m_fp <- m %>% fitBounds(fpBBox[1,1], fpBBox[2,1], fpBBox[1,2], fpBBox[2,2])

## Add polygons
m_fp <- m_fp %>% addPolygons(data=fpLL, fill=FALSE, stroke=TRUE, color=c("yellow", "LightPink")[1], weight=2, dashArray="1,2")

## Display HTML Widget
m_fp
```

## WebODM Results

<iframe scrolling="no" title="WebODM" width="100%" height="600" frameBorder="1" src="`r stchLst$IFrameSrc`"></iframe>

_Assessment_: `r stchLst$Assessment`

## Pix4Dmapper Orthomosaic

<iframe scrolling="no" title="WebODM" width="100%" height="600" frameBorder="1" src="`r stchLst$P4Dtiles`"></iframe>


